%-------------------------
% Resume in Latex
% Author : Kamal
% Based off of: https://github.com/imkamaladhikari/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% Professional Color Palette Definitions
\definecolor{primarynavy}{HTML}{1A365D} % Deep Navy for Section Headers
\definecolor{iconaccent}{HTML}{4A5568}  % Deep Slate Blue for Icons
\definecolor{linkedinblue}{HTML}{0077B5} % Official LinkedIn Blue (Kept for the profile link)
\definecolor{light-grey}{HTML}{E2E8F0}  % Light grey boundary line
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{0.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Professional Sans Serif Section Titles
\titleformat{\section}{
    \color{primarynavy}\bfseries\vspace{4pt}\raggedright\large
}{}{0em}{}[\color{light-grey}{\titlerule[1.5pt]}\vspace{-3pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ 
      \textit{#3} & {\color{dark-grey}\small #4}\\ 
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \color{primarynavy} KAMAL SINGH} \\ \vspace{6pt}
    \small 
    \textcolor{iconaccent}{\faPhone*} \texttt{ +91 8285008438} \hspace{4pt} $|$ \hspace{4pt}
    \textcolor{iconaccent}{\faEnvelope} \hspace{2pt} \texttt{kamal.singh.adhikari@outlook.com} \hspace{4pt} $|$ \hspace{4pt}
    \href{https://www.linkedin.com/in/imkamaladhikari}{\textcolor{linkedinblue}{\faLinkedin} \texttt{ imkamaladhikari}} \hspace{4pt} $|$ \hspace{4pt}
    \textcolor{iconaccent}{\faMapMarker*} \hspace{2pt} \texttt{New Delhi, India}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Implementation Consultant}{April 2024 -- Present}
      {\href{https://triotree.com/}{\myuline {TrioTree Technologies Pvt Ltd}}}{Noida, India}
      
      \resumeItemListStart
        \resumeItem{Lead end-to-end healthcare IT implementations across multiple hospitals, ensuring on-time and error-free go-lives.}
        \resumeItem{Translate business requirements into actionable implementation plans and precise software configuration strategies.}
        \resumeItem{Collaborate with clients, developers, and QA teams to ensure seamless deployment and post-go-live stability.}
        \resumeItem{Manage technical teams to perform SQL data fixes, stored procedure updates, and system integrations improving performance and reliability.}
        \resumeItem{Oversee project deliverables, monitor progress, and proactively mitigate risks to ensure successful project completion.}
        \resumeItem{Delivered 10+ HIS/LIS implementations on schedule with zero major post-go-live issues.}
        \resumeItem{Directed SQL optimization and stored procedure revisions, enhancing system performance by 20\%.}
        \resumeItem{Designed and executed 100+ test cases, reducing post-go-live defects by 30\%.}
        \resumeItem{Led legacy data migration and cleansing initiatives with 100\% accuracy.}
        \resumeItem{Implemented LIS machine interfacing, reducing lab turnaround times by 25\%.}
        \resumeItem{Authored Business Requirement Documents (BRDs), logged and validated 50+ bugs, ensuring smooth coordination with the product and development teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Associate Business Analyst}{May 2023 -- April 2024}
      {\href{https://triotree.com/}{\myuline {TrioTree Technologies Pvt Ltd}}}{Noida, India}
      \resumeItemListStart
        \resumeItem{Collected requirements from 10+ hospital departments; configured HIS/LIS modules accordingly.}
        \resumeItem{Created \& executed 150+ manual test cases (Billing, Radiology, LIS etc), cutting error recurrence by 40\%.}
        \resumeItem{Coordinated bug resolution with developers, achieving a 20\% faster closure rate.}
        \resumeItem{Optimized SQL queries \& validated migrated data with 100\% accuracy. Authored BRDs and reusable test cases, boosting QA efficiency by 35\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Associate Business Analyst (Trainee)}{May 2022 -- May 2023}
      {\href{https://triotree.com/}{\myuline {TrioTree Technologies Pvt Ltd}}}{Noida, India}
      \resumeItemListStart
        \resumeItem{Supported 10+ LIS/HIS migration projects, ensuring zero discrepancies in legacy-to-HIS data transfer.}
        \resumeItem{Assisted in configuring 30+ LIS machine interfaces, reducing reporting delays.}
        \resumeItem{Conducted defect testing \& retesting, ensuring 95\% bug resolution pre-go-live.}
        \resumeItem{Delivered client training \& support, driving 90\% user adoption within 3 months.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Key Achievements (Across Roles)}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Healthcare IT Migrations}}{Jan. 2024 -- Present}
       \resumeItemListStart
      \resumeItem{Successfully implemented healthcare IT systems in 10+ hospitals PAN India}
          \resumeItem{Reduced deployment timelines by 70\% through optimized rollout strategies.}
          \resumeItem{Executed 100+ test cases, logged and resolved 200+ system bugs across hospital implementations.}
          \resumeItem{Configured LIS machine interfaces (ASTM protocol) and automated notifications (SMTP/API).}
          \resumeItem{Ensured smooth SQL data migration for 1M+ patient records with $<$1\% error rate.}
       \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IGNOU University}{}
      {Bachelor of Computer Application (BCA)}{New Delhi, India}
      
    \resumeSubheading
      {Diploma}{}
      {Master Diploma in Software Engineering}{New Delhi, India}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Core Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Project Management:} {Deployment Planning, Workflow Mapping, UAT, Stakeholder Engagement} \vspace{2pt} \\
        \textbf{Healthcare IT:} {HIS, EMR, Radiology, Billing, Inventory, Laboratory Systems} \vspace{2pt} \\
        \textbf{Testing \& Quality Assurance:} {Manual Testing, Test Case Design, Bug Reporting, Defect Tracking} \vspace{2pt} \\
        \textbf{Technical Skills:} {SQL Queries \& Procedures, Data Fixing, Legacy Data Migration, Master Data Setup} \vspace{2pt} \\
        \textbf{System Configuration:} {IIS, SMTP, ASTM Interfaces, API Integrations} \vspace{2pt} \\
        \textbf{Documentation:} {Requirement Gathering, SRS, BRD, Gap Analysis, Workflow Mapping}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}